\documentclass{article}

% General document formatting
\usepackage{url}
% \usepackage[margin=0.7in]{geometry}
% \usepackage[parfill]{parskip}
% \usepackage[utf8]{inputenc}

% Related to math
\usepackage{amsmath,amssymb,amsfonts,amsthm}

\begin{document}

\section*{Differences between submissions}

We had little time to validate the method so we really just used the 7 submissions
to randomly tweak some features and parameters.  We had several different
features derived from neural networks that we felt were important so we tried
several of these. We didn't have time to play with the gradient boosting machine
parameters much so we just tried a few different options.  Each submission was
identical to the previous one excepting the details noted below.

\subsection*{Submission 1}

Submission 1 used features derived from the original DeepSea network, DNase,
conservation and stacked \texttt{Value} and \texttt{Confidence} predictions.


\subsection*{Submission 2}

Submission 2 replaced the original DeepSea network features with features
derived from a network learned by Daniel Quang on the same task.


\subsection*{Submission 3}

Submission 3 replaced the Daniel Quang network features with features derived
from a network learned by ourselves on the same task.


\subsection*{Submission 4}

Submission 4 changed the parameters for the gradient boosting machine.  We used
Bayesian optimisation to determine these.


\subsection*{Submission 5}

Submission 5 retained the new gradient boosting machine parameters but went
back to using the original DeepSea features.


\subsection*{Submission 6}

Submission 6 changed the \texttt{max\_depth} gradient boosting machine parameter
to 9.


\subsection*{Submission 7}

Submission 7 went back to using the original gradient boosting machine parameters
but keeping \texttt{max\_depth} at 9.



\end{document}
